Hydras \& Co.

### 2023-06-20 doc/chapter-fol.tex
fix a latex error
small changes in documentation

Structural induction/recursion principles are generated by 
\texttt{Formula}'s definition, for instance:

\inputsnippets{FolExamples/FormulaRect}

@@

\inputsnippets{folProp/freeVarF, FolExamples/freeVarEx}

\begin{remark}
  Note that \texttt{freeVarF} is defined by cases over the basic connectives. In the following example, the connective \texttt{<->} is expanded into a conjunction of two implications, thus the 
list returned by \texttt{freeVarF} may contain redundancies.

@@

>>>>

Structural induction/recursion principles are generated from
\texttt{Term}, \texttt{Terms} and \texttt{Formula}'s definition, for instance:

\inputsnippets{fol/TermSchemes, FolExamples/FormulaRect}

@@

Concerning formulas, the treatement of binding is realized 
whith the help of \texttt{List} library function \texttt{remove}.
\inputsnippets{folProp/freeVarF, FolExamples/freeVarEx}

\begin{remark}
  Note that \texttt{freeVarF} is defined by cases over the \emph{basic} connectives. Formulas with contain \texttt{iffH} or
\texttt{ifThenElseH} are expanded before the application of
\texttt{freevarF}, and the 
list returned by \texttt{freeVarF} may contain redundancies.

@@

\begin{todo}
  Present \texttt{substT} and \texttt{substTs} as structurally recursive functions. Then show \texttt{BadSubst.v} and motivate
 depth induction.
\end{todo}

\inputsnippets{folProp/subsTdef}

\inputsnippets{BadSubst/BadSubstFdef}

\inputsnippets{BadSubst/BadSubstFexample}
